\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
    \setmainfont[]{Liberation Serif}
    \setsansfont[]{Liberation Sans}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[normalem]{ulem}
% avoid problems with \sout in headers with hyperref:
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

First came the stars: And from them was birthed their father, for all was naught and life was upside down. Their shine was the first hint of light to be seen, and the one that guided the moon to it's first orbit. It was with this that night was made.

Once that the moon had come the light was too weak still, so at first the moon fell with an aching song but then hung by the thin silver threads that the stars had strung around his neck, and his swinging from the threads was the second orbit of the moon: ????? in their own tongue or ??????????????? \footnote{Which one? Whose?}

And with the swaying and swinging of the father-son a firmness-before-the-moon was needed, so next came the elder sister: twilight, stone-and-mortar. Twilight had no orbits or swaying and hung from no threads that it did not choose to, and it was in this firmness and confidence that she became liaison between god and mortal, and the first holder of the spark.

Being preceded by twilight gave the night moon respite for he could now lay his legs on her land\footnote{Note to self: Find more text in this language to confirm if it's actually saying ``Land.''}, and he trashed much less as he swung. This was his third orbit.\footnote{And this one doesn't have weird names like the second? \sout{Where's the first?}}

Twilight then tried to use her spark to lay light upon the land so that the minds and hearts of all could see:\footnote{Where are mortals made in this whole creation myth? The lack of explanation on the mater is something very typical gri\sout{ph}ffonish myth, but at the same time night being the first to exist is almost exclusive of moonlet lore, which, I am not sure moonlets existed at the time this was written.} But the spark, however nurtured it was, was not made for such things. \footnote{What was it made for then? And where have I read about a spark before?} And while twilight understood that she had misused the spark and nearly broken it and herself, she was greatly displeased not because of her own misuse, but because of the inadequacy of her tools.

And this is why the first halves of the dualities were flawed.

\begin{quote}
And this just ends there. Is this some kind of mythological meta joke?
\end{quote}

\end{document}
